---
title: "Research"
lightbox: true
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE,eval=FALSE}
#| echo: false
#| warning: false
#| message: false

library(pacman)
pacman::p_load(
  tidyverse,
  here,
  knitr,
  kableExtra,
  RefManageR,
  httr,
  fontawesome
  )

#library(dplyr)
#library(knitr)

#source(here("Rfunctions","BibForQuarto.R"))  # Saved function in this file

# Fetch the BibTeX file from GitHub
bib_url <- "https://raw.githubusercontent.com/arthurheim/Data_DrivenResume/main/Data/publi_heim.bib"
response <- GET(bib_url)
bib_content <- content(response, "text")

# Write the content to a temporary file
temp_file <- tempfile(fileext = ".bib")
writeLines(bib_content, temp_file)

# Read the temporary BibTeX file
bib <- ReadBib(temp_file, check = FALSE) %>% as.tibble() #%>% distinct(title,.keep_all = TRUE) %>% 
 # mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

```

```{r , include=FALSE, eval=FALSE}
#| echo: false
#| warning: false
#| message: false

# library(RefManageR)
# library(httr)
# 
# 
# # Function to filter and print references based on key conditions
# print_refs <- function(bib, condition) {
#   filtered <- bib[function(x) eval(parse(text = condition), envir = list(key = x$key))]
#   PrintBibliography(filtered, .opts = list(check.entries = FALSE, sorting = "ydnt"))
# }
```

## Early childhood education and care

### Pre-prints

::: {.callout-tip}
## Conditionally accepted !
-   Carbuccia, L. Heim, A. Barone, C. & Chevalier, C. (2025) [Investigating how administrative burden and search costs affect social inequalities in early childcare access, a randomised controled trial](https://osf.io/rh7eb/?view_only=ef7409ac646544eaac946374de134892), *Nature Human Behaviour*.

    -   "Multi-arm RCT in the Paris region measuring the effects of providing information and administrative support to pregnant women to access formal childcare. The programme increases social inequalities in access to daycare centres.

        -   [Pre-print and replication material](https://osf.io/rh7eb/?view_only=ef7409ac646544eaac946374de134892)
        -   [Pre-registration](https://www.socialscienceregistry.org/trials/9901)
:::

-   Combe, J. & Heim, A. (2024) [Rage against the Matching: Fairness and inequalities in a market design experiment in France](https://www.dropbox.com/scl/fi/7r9c1lglfu04naqnbad4c/CombeHeim2024.pdf?rlkey=44rkwhus5nwj9kjq0gn0l4w9b&dl=0 "Rage against the Matching: Fairness and inequalities in a market design experiment in France"), in *Social investment & the changing face of poverty: Essays on the design & Evaluation of family policies in France*, PhD Thesis, EHESS, 2024. English.

    -   Definition and implementation of market design solutions to define assignment mechanisms for the daycare market in a field experiment in France. Analysis of the effect of priority weights and behavioural responses to incentives.
        -   [Slides](https://www.dropbox.com/scl/fi/4pvg0chbiwtevwiil5re5/RATM_EN092024.pdf?rlkey=o67gk9trd2pqof8jh6mjjpbz7&dl=0)
        -   [Chapter](https://www.dropbox.com/scl/fi/7r9c1lglfu04naqnbad4c/CombeHeim2024.pdf?rlkey=44rkwhus5nwj9kjq0gn0l4w9b&dl=0)

## Active labour market policies

### Pre-prints

::: {.callout-tip}
## New version !
-   Heim (2025) [Welfare to What ?](https://osf.io/y8stq) "Welfare to what ? Experimental evaluation of an activation programme for single mothers in poverty in France"), submitted to *European Economic Review*.

    -   A Randomised experiment of an intensive welfare-to-work programme targetting single parents on long-term welfare in France. Results show no effect on labour market participation and poverty after the end of the programme but higher social transfers.

        -   [Pre-print and replication material](https://osf.io/qhazf/)
        -   [Pre registration](https://www.socialscienceregistry.org/trials/5930)
        -   [Slides](https://www.dropbox.com/scl/fi/g7815ngs3mrv2kqb7tjqz/WtW_Slides_052025_EN.pdf?rlkey=rc7vxy07c6eal2b048ayiq5df&dl=0)

    -   Press coverage :

        -   [**Mediapart**](https://www.mediapart.fr/journal/economie-et-social/120125/reforme-du-rsa-la-menace-de-marginaliser-des-publics-deja-vulnerables)
        -   [**Alternatives économiques**](https://www.alternatives-economiques.fr/rsa-conditionne-preuve-trois-ca-ne-marche/00113744)
:::

-   Galitzine, A. & Heim, A. [Tax burden on the poor: : Single mothers’ optimisation behaviours following an experimental activation programme in France](https://www.dropbox.com/scl/fi/xdhov425ez5n1jcxl053r/GalitzineHeim2024.pdf?rlkey=pdun971icjt4biq7ikwrm2ji1&dl=0) in *Social investment & the changing face of poverty: Essays on the design & Evaluation of family policies in France*, PhD Thesis, EHESS, 2024. English.

    -   We challenge the idea that the French tax-benefit system "make work pay" for single parents and analyse reactions following a randomised intensive welfare-to-work programme. We use instrumental distribution regressions and find strong (negative) intensive margin reactions.

        -   [Pre-print](https://www.dropbox.com/scl/fi/xdhov425ez5n1jcxl053r/GalitzineHeim2024.pdf?rlkey=pdun971icjt4biq7ikwrm2ji1&dl=0)
        -   [Slides](https://www.dropbox.com/scl/fi/9dbpmcefmout7rwrwqvt6/TaxBurdenEnShort.pdf?rlkey=omrpuo36dge0phkd2havhxo5p&dl=0)

## Education

### Book

-   Heim, A, Steinmetz, C. & Tricot, A. (2015) [Faut-il encore redoubler ?](https://www.reseau-canope.fr/notice/faut-il-encore-redoubler.html), Éditions Canopé.

    -   This book builds on the Conference of Consensus on grade repetition organised by the National council for the Evaluation of the French schooling system (Cnesco) from 2013 to 2014. It summarised the state of research at that time and the recommendations from the Jury.

### Working papers in French

-   Mons, N., Heim, A., & Blanchard‐Schneider, A. (2015). [Lutter contre les difficultés scolaires : Le redoublement et ses alternatives](https://hal.science/hal-04623894v1). Dossier de synthèse. Cnesco.

-   Heim, A., & Steinmetz, C. (2015). [Une comparaison statistique et reglementaire.](https://www.cnesco.fr/wp-content/uploads/2015/01/partie_1.pdf) In Lutter conte la difficulté scolaire: Le redoublement et ses alternatives (Vol. 1). Conseil national d’évaluation du système scolaire (Cnesco).

-   Heim, A., & Steinmetz, C. (2015). [De l’étude de ses impacts à la croyance en son utilité.](https://www.cnesco.fr/wp-content/uploads/2015/01/part_2.pdf) In Le redoublement en France et dans le monde (Vol. 2). Conseil national d’évaluation du système scolaire (Cnesco).

-   Heim, A., & Steinmetz, C. (2015). [Quelles alternatives au redoublement ?](https://www.cnesco.fr/wp-content/uploads/2015/01/partie_3.pdf) In Le redoublement en France et dans le monde (Vol. 3). Conseil national d’évaluation du système scolaire (Cnesco).

-   Heim, A., & Galinié, A. (2016). [Inégalités scolaires : Quels rôles jouent les cours privés ?](https://www.cnesco.fr/wp-content/uploads/2016/09/heim_galine_solo1.pdf) In Contribution au rapport du Cnesco: Les inégalités scolaires d’origines sociales et ethnoculturelle. Cnesco.

-   Heim, A. & Ni J. (2016) [L'éducation peut elle favoriser la croissance ?](https://www.strategie.gouv.fr/publications/leducation-favoriser-croissance) Note d'analyse, France Stratégie.

-   Heim, A. (2018). [Quand la scolarisation à 2 ans n’a pas les effets attendus: Des evaluations sur données françaises](https://www.strategie.gouv.fr/sites/strategie.gouv.fr/files/atoms/files/dt-scolarisation-precoce-2-ans-janvier.pdf) Document de travail, France Stratégie.

## Social investment

### PhD Thesis

-   Heim, A. (2024) [Social investment and the changing face of poverty: essay on the design and evaluation of family and social policies in France](https://hal.science/tel-04801852), PhD Thesis. Paris School of Economics (EHESS), English. ⟨NNT : ⟩. ⟨tel-04801852⟩

### Working papers

-   Fougère, D. & Heim, A (2019) [L'évaluation socioéconomique de l'investissement social](https://hal.science/hal-03456048v1)

-   Fougère, D. & Heim, A (2019) [L'investissement social à l'épreuve de l'évaluation socioéconomique](https://hal.science/hal-03474890v1) Document de travail, France Stratégie - Commissariat général à la stratégie et la prospective. 2019, pp.8. ⟨hal-03474890⟩

-   Heim, A. (2017). [Comment estimer le rendement de l’investissement social ?](https://www.strategie.gouv.fr/sites/strategie.gouv.fr/files/atoms/files/fs_dt2017-02_rendement_investissement_social.pdf) Document de Travail France Stratégie, 2017‐02.

-   Heim, A. (2017). L’investissement social: quelles significations ? Quelles implications ? *Cahier Français*, 399, 16–21.
