---
title: "Publications"
lightbox: true
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE,eval=FALSE}
#| echo: false
#| warning: false
#| message: false

library(pacman)
pacman::p_load(
  tidyverse,
  here,
  knitr,
  kableExtra,
  RefManageR,
  httr
  )

#library(dplyr)
#library(knitr)

#source(here("Rfunctions","BibForQuarto.R"))  # Saved function in this file

# Fetch the BibTeX file from GitHub
bib_url <- "https://raw.githubusercontent.com/arthurheim/Data_DrivenResume/main/Data/publi_heim.bib"
response <- GET(bib_url)
bib_content <- content(response, "text")

# Write the content to a temporary file
temp_file <- tempfile(fileext = ".bib")
writeLines(bib_content, temp_file)

# Read the temporary BibTeX file
bib <- ReadBib(temp_file, check = FALSE) %>% as.tibble() #%>% distinct(title,.keep_all = TRUE) %>% 
 # mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

```

```{r , include=FALSE, eval=FALSE}
#| echo: false
#| warning: false
#| message: false

# library(RefManageR)
# library(httr)
# 
# 
# # Function to filter and print references based on key conditions
# print_refs <- function(bib, condition) {
#   filtered <- bib[function(x) eval(parse(text = condition), envir = list(key = x$key))]
#   PrintBibliography(filtered, .opts = list(check.entries = FALSE, sorting = "ydnt"))
# }
```

## Working Papers

### 2024

-   [Rage against the Matching](https://www.dropbox.com/scl/fi/7r9c1lglfu04naqnbad4c/CombeHeim2024.pdf?rlkey=44rkwhus5nwj9kjq0gn0l4w9b&dl=0 "Rage against the Matching: Fairness and inequalities in a market design experiment in France") (with Julien Combe)

We use market design to define assignment mechanisms for the daycare market. We conduct a field experiment using them in France and analyse *who gets what and why.*

-   [Welfare to What ?](https://www.dropbox.com/scl/fi/8jmyo6vvo4sk8o2ru09tw/Heim2024.pdf?rlkey=3cq7y8o84npws5cmdm2pgfsbx&dl=0 "Welfare to what ? Experimental evaluation of an activation programme for single mothers in poverty in France")

I evaluate a randomised experiment of an intensive welfare-to-work programme targetting single parents on long-term welfare in France. I find no effect on labour market participation and poverty after the end of the programme.

-   [Tax burden on the poor](https://www.dropbox.com/scl/fi/xdhov425ez5n1jcxl053r/GalitzineHeim2024.pdf?rlkey=pdun971icjt4biq7ikwrm2ji1&dl=0 "Tax burden on the poor: Single mothers’ optimisation behaviours following an experimental activation programme in France") (with Alexandra galitzine)

We challenge the idea that the French tax-benefit system "make work pay" for single parents and analyse reactions following a randomised intensive welfare-to-work programme.

------------------------------------------------------------------------

# Older publications

## Book

### 2015

-   [Faut-il encore redoubler ?](https://www.reseau-canope.fr/notice/faut-il-encore-redoubler.html) (With André Tricot and Claire Steinmetz)

This book builds on the Conference of Consensus organised by the National council for the Evaluation of the French schooling system (Cnesco) from 2013 to 2014. It summarised the state of research at that time and the recommendations of the Jury.

## Pre-doctoral Research and Policy Briefs

**Empty for now, see my CV**

**This website is currently being built and is regularly updated.**
